Type-Safe Modular Parsing

### 2017-01-14 paper/sections/Inheritance.tex
Typos in 1234.

\paragraph{Conflicts and/or ambiguity} As we demonstrated before, the longest match alternative combinator is useful when composing parsers. However, ambiguous grammars still cause subtle issues in modular parsing. For example, if \inlinecode{parserA} and \inlinecode{parserB} accept a same string but generate different results, then the result of \inlinecode{parserA ||| parserB} really depends on the implementation of the alternative combinator, because the results can not be prioritized by length. Since the composition is handled explicitly by user, conflicts could be resolved by overriding ambiguous parsing code, using the pattern discussed in Section~\ref{subsec:overriding-rules}.

>>>>

\paragraph{Conflicts and/or ambiguity} As we demonstrated before, the longest match alternative combinator is useful when composing parsers. However, ambiguous grammars still cause subtle issues in modular parsing. For example, if \inlinecode{parserA} and \inlinecode{parserB} accept a same string but generate different results, then the result of \inlinecode{parserA ||| parserB} really depends on the implementation of the alternative combinator, because the results can not be prioritized by length. Since the composition is handled explicitly by a user, conflicts could be resolved by overriding ambiguous parsing code, using the pattern discussed in Section~\ref{subsec:overriding-rules}.

### 2017-01-14 paper/sections/PackratParsing.tex
Typos in 1234.

After left-recursion elimination, the structure of grammar is changed,
as well as its corresponding parser. In a modular setting, it is
possible but unnecessarily complicated to analyse the grammar and
rewrite it when doing extension. Anticipating that every non-terminal
has left-recursive rules is helpful for extensibility but overkill,
since it is inconvenient and introduces extra complexity for
representation of grammar and implementation of parser.

@@

\paragraph{Longest Match Composition} Another problematic issue
in parser combinator libraries is the need for manually prioratizing/ordering
alternatives in a grammar.
Consider the grammar:
\setlength{\grammarindent}{5em}
\begin{grammar}
<expr> ::= <int> \alt <int> `+' <expr>
\end{grammar}

@@

\noindent However, this results in the worst case exponential time
complexity in Parsec, because it does not provide optimizations
for backtracking.

>>>>

After left-recursion elimination, the structure of grammar is changed,
as well as its corresponding parser. In a modular setting, it is
possible but unnecessarily complicated to analyse the grammar and
rewrite it when doing extensions. Anticipating that every non-terminal
has left-recursive rules is helpful for extensibility but overkill,
since it is inconvenient and introduces extra complexity for
representation of a grammar and implementation of a parser.

@@

\paragraph{Longest Match Composition} Another problematic issue
in parser combinator libraries is the need for manually prioritizing/ordering
alternatives in a grammar.
Consider the grammar:
\setlength{\grammarindent}{5em}
\begin{grammar}
<expr> ::= <int> \alt <int> `+' <expr>
\end{grammar}

@@

\noindent However, this results in the worst-case exponential time
complexity in Parsec, because it does not provide optimizations
for backtracking.
